\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-12-10 tex/paper.tex
Added some biba sections

\subsection{Design}
\fix Mathematical formal description of how the system works

@@

\subsubsubsection{API}
In this work a RESTful API was implemented and used for back-end $\Leftrightarrow$ front-end
communication.

@@

%What to write about
%Battle Binar
y
%Security features of CDN's
%What is needed by the logic, like what happens after two consecutive deletes
%
%What is needed
%* Security layers
%* snapshots
%* Virtual file structure
%* Versioning of content
%* Multi project support
%* Auth and audit logs
%* Users

>>>>

\subsection{Elements of the Model}
\fix Mathematical formal description of how the system works

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        Set & Elements & semantics \\ \hline
        C   & $c_0\dots c_n$                & Containers; folders in the virtual file system\\ \hline
        F   & $f_0\dots f_n$                & Files; files, images, videos\\ \hline
        P   & $p_0\dots p_n$                & Content; Meta-data for files\\ \hline
        U   & $u_0\dots u_n$                & Users; registered users in the system\\ \hline
        A   & $A[u_0,c_0]\dots A[u_n, c_n]$ & Access matrix; describes what containers users have access to\\ \hline
    \end{tabular}
\end{center}

\subsection{Access rights}
\begin{equation}
    \begin{split}
        u \in U \text{ can read } c \in C & \Iff u \in A[u,c] \\
        u \in U \text{ can write } c \in C & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \in U \text{ can delete } p \in c & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \nexists U \text{ can delete } f \in F \\
        \forall c \in C, \quad \exists u \in U & \mid a \in A[u,c] 
    \end{split}
\end{equation}

\subsection{Data integrity}
A computer system or subsystem is defined as possessing the property of integrity if it behaves consistently
according to a defined standard. This implies that a subsystem possessing the property of integrity
does not guarantee an absolute behaviour of the system, but rather that it performs according to
what its creator intended ~\cite{BIBA}.

\subsection{Initial Assumptions}
To create an integrity model, some initial assumptions have to be made about what the correct behaviour
of the system is, which the model then can be shown to follow. In this work unintentional behaviour
as the result of data modification is the main concern, which could be used for sabotage or simply be the
effect unintentional unfortunate race conditions etc.

\subsection{Integrity Threats}
According to Biba et. al~\cite{BIBA} one can consider two threat sources, namely subsystem external
and subsystem internal. The external sources could be another system calling the subsystem with
faulty data or trying to make inaccurate calls to program functions, it could also be somebody
trying to tamper with the exposed functions of the program. Threats that are internal could be a
malicious part of the subsystem or simply an incorrect part of the subsystem, which does not behave
according to specification.

In this work external threats are handled as threats that can occur from what has been exposed by
the API (See Section~\ref{sec:API} and internal threats as incorrect implementation. As the server
and its system are assumed safe malicious subsystems are not considered.

\fix Translate to mathematical expressions

\begin{itemize}
    \item if a user wants to update a file in a content, the file is copied and the original is intact
    \item if a user reads content and then writes to it, the content is directly changed
    \item if a user copies content, a new content is created at the destination with reference to the same
          file
    \item if a user reads from a container and then writes to it, the container is directly changed
          (Which means last write wins, which doesn't matter)
    \item if a user copies a container, the full container tree is re created with new ids at the destination,
          its content still refers to the same files.
\end{itemize}

@@

\subsubsubsection{API}
\label{sec:API}
In this work a RESTful API was implemented and used for back-end $\Iff$ front-end
communication.

@@

%What to write about
%Battle Binary
%Security features of CDN's
%What is needed by the logic, like what happens after two consecutive deletes
%
%What is needed
%* Security layers
%* snapshots
%* Virtual file structure
%* Versioning of content
%* Multi project support
%* Auth and audit logs
%* Users
